%==============================================================================
\section{Introduction}
%==============================================================================
% Structure follows the supervisor's 5-paragraph / 9-sentence template:
% hook, gap, study (+RQs), contribution, roadmap.

Large language models (LLMs) built on the Transformer architecture \cite{vaswani2017attention} now power knowledge-intensive applications such as question answering, search, and code assistance, yet their parametric knowledge is frozen at training time and they often hallucinate, producing fluent text that is factually wrong \cite{ji2023survey}. Retrieval-Augmented Generation (RAG) \cite{lewis2020rag} addresses this by retrieving documents from an external corpus and conditioning generation on them, and it has become a default pattern for deploying LLMs over private or fast-changing knowledge \cite{gao2024retrieval}.

Grounding generation in retrieved text creates a new dependency: the answer is only as trustworthy as the corpus behind it. Standard RAG assumes a benign knowledge base, and existing evaluation frameworks such as RAGAS \cite{es2024ragas} and ARES \cite{saadfalcon2024ares} measure faithfulness to the retrieved context rather than the integrity of that context. In open-world deployments, however, an adversary can insert malicious documents through knowledge poisoning \cite{zou2024poisoned}; injecting only five malicious passages per question into a corpus of millions ($\approx$0.0002\%) can drive attack success to roughly 90\%. A system that answers faithfully from a poisoned document therefore scores well under current metrics while emitting compromised output. We call this the \emph{Security-Reliability Gap}: high semantic relevance is treated as a proxy for truth, and the few available poisoning defenses are mostly offline corpus-cleaning steps with no online trust layer inside the inference loop.

This paper presents an \emph{Evaluation Agent} that closes this gap. It acts as defensive middleware that screens retrieved context before generation and outputs an interpretable \emph{Trust Index} that fuses Natural Language Inference (NLI) factual verification, a five-signal poison detector, and a cross-document consistency estimate. We evaluate the agent on two public benchmarks (TruthfulQA and FEVER) across three LLMs and four attack strategies, and then apply it to a software-engineering use case, a secure-coding assistant that retrieves from guidance based on the Open Worldwide Application Security Project (OWASP) Top~10 and the Common Weakness Enumeration (CWE). We study three research questions:
\begin{itemize}
  \item \textbf{RQ1.} How effectively does the Evaluation Agent detect misinformation and knowledge poisoning in retrieved context?
  \item \textbf{RQ2.} How does NLI-based factual verification change the trustworthiness of RAG output?
  \item \textbf{RQ3.} How resilient is the approach across LLMs, datasets, and attack strategies, including a secure-coding setting in the software-development lifecycle (SDLC)?
\end{itemize}

We find that the agent detects overt poisoning well (100\% recall on instruction injection, 91\% accuracy and 100\% precision on TruthfulQA mixed attacks) but that in-place edits such as entity swaps and subtle weakening stay near-undetectable, which is a limit of surface-signal detection rather than of tuning. We also show that NLI-based trust scoring depends on the generating LLM, and that generation style matters more than model size: a 7B model reaches 87\% accuracy while a 35B model whose hedged answers depress NLI entailment falls to 69\%. Detection is stable across repeated runs and invariant to retrieval depth, and a weaker FEVER result bounds external validity. These findings extend prior RAG evaluation, which checks faithfulness to context, by adding an online check on the integrity of that context, and they map where such checks succeed and where world-knowledge verification is still needed.

%The remainder of the paper is organized as follows. Section~II reviews background and related work. Section~III presents the Evaluation Agent, threat model, and Trust Index. Section~IV describes the experimental design, Section~V reports results, Section~VI discusses implications and limitations, and Section~VII concludes.
