%==============================================================================
% References (manual IEEE-style bibliography for a self-contained draft;
% switch to BibTeX/biblatex with reference.bib if preferred).
%==============================================================================
\begin{thebibliography}{00}
\bibitem{vaswani2017attention} A. Vaswani \emph{et al.}, ``Attention is all you need,'' in \emph{Adv. Neural Inf. Process. Syst. (NeurIPS)}, vol.~30, 2017, pp.~5998--6008.
\bibitem{ji2023survey} Z. Ji \emph{et al.}, ``Survey of hallucination in natural language generation,'' \emph{ACM Comput. Surv.}, vol.~55, no.~12, Art.~no.~248, pp.~1--38, 2023.
\bibitem{lewis2020rag} P. Lewis \emph{et al.}, ``Retrieval-augmented generation for knowledge-intensive NLP tasks,'' in \emph{Adv. Neural Inf. Process. Syst. (NeurIPS)}, vol.~33, 2020, pp.~9459--9474.
\bibitem{zou2024poisoned} W. Zou, R. Geng, B. Wang, and J. Jia, ``PoisonedRAG: Knowledge corruption attacks to retrieval-augmented generation of large language models,'' in \emph{Proc. 34th USENIX Security Symp.}, 2025, pp.~3827--3844.
\bibitem{es2024ragas} S. Es, J. James, L. Espinosa-Anke, and S. Schockaert, ``RAGAs: Automated evaluation of retrieval augmented generation,'' in \emph{Proc. 18th Conf. Eur. Chapter ACL (Demos)}, 2024, pp.~150--158.
\bibitem{saadfalcon2024ares} J. Saad-Falcon, O. Khattab, C. Potts, and M. Zaharia, ``ARES: An automated evaluation framework for retrieval-augmented generation systems,'' in \emph{Proc. NAACL}, 2024, pp.~338--354.
\bibitem{gao2024retrieval} Y. Gao \emph{et al.}, ``Retrieval-augmented generation for large language models: A survey,'' \emph{arXiv:2312.10997}, 2024.
\bibitem{asai2024selfrag} A. Asai, Z. Wu, Y. Wang, A. Sil, and H. Hajishirzi, ``Self-RAG: Learning to retrieve, generate, and critique through self-reflection,'' in \emph{Int. Conf. Learn. Represent. (ICLR)}, 2024.
\bibitem{karpukhin2020dense} V. Karpukhin \emph{et al.}, ``Dense passage retrieval for open-domain question answering,'' in \emph{Proc. EMNLP}, 2020, pp.~6769--6781.
\bibitem{lin2022truthfulqa} S. Lin, J. Hilton, and O. Evans, ``TruthfulQA: Measuring how models mimic human falsehoods,'' in \emph{Proc. 60th Annu. Meeting ACL}, 2022, pp.~3214--3252.
\bibitem{honovich2022true} O. Honovich \emph{et al.}, ``TRUE: Re-evaluating factual consistency evaluation,'' in \emph{Proc. NAACL}, 2022, pp.~3905--3920.
\bibitem{greshake2023indirect} K. Greshake \emph{et al.}, ``Not what you've signed up for: Compromising real-world LLM-integrated applications with indirect prompt injection,'' in \emph{Proc. 16th ACM Workshop Artif. Intell. Secur.}, 2023, pp.~79--90.
\bibitem{shuster2021retrieval} K. Shuster, S. Poff, M. Chen, D. Kiela, and J. Weston, ``Retrieval augmentation reduces hallucination in conversation,'' in \emph{Findings of ACL: EMNLP}, 2021, pp.~3784--3803.
\bibitem{thorne2018fever} J. Thorne, A. Vlachos, C. Christodoulopoulos, and A. Mittal, ``FEVER: A large-scale dataset for fact extraction and verification,'' in \emph{Proc. NAACL}, 2018, pp.~809--819.
\bibitem{reimers2019sentence} N. Reimers and I. Gurevych, ``Sentence-BERT: Sentence embeddings using Siamese BERT-networks,'' in \emph{Proc. EMNLP-IJCNLP}, 2019, pp.~3982--3992.
\bibitem{pearce2022} H. Pearce, B. Ahmad, B. Tan, B. Dolan-Gavitt, and R. Karri, ``Asleep at the keyboard? Assessing the security of GitHub Copilot's code contributions,'' in \emph{Proc. IEEE Symp. Security and Privacy (S\&P)}, 2022, pp.~754--768.
\bibitem{perry2023} N. Perry, M. Srivastava, D. Kumar, and D. Boneh, ``Do users write more insecure code with AI assistants?'' in \emph{Proc. ACM SIGSAC Conf. Computer and Communications Security (CCS)}, 2023, pp.~2785--2799.
\bibitem{owasp2021} OWASP Foundation, ``OWASP Top 10 (2021).'' [Online]. Available: https://owasp.org/Top10/2021/
\bibitem{mitrecwe} MITRE, ``Common Weakness Enumeration (CWE).'' [Online]. Available: https://cwe.mitre.org/
\bibitem{guu2020realm} K. Guu, K. Lee, Z. Tung, P. Pasupat, and M. Chang, ``REALM: Retrieval-augmented language model pre-training,'' in \emph{Proc. 37th Int. Conf. Machine Learning (ICML)}, 2020, pp.~3929--3938.
\bibitem{izacard2021fid} G. Izacard and E. Grave, ``Leveraging passage retrieval with generative models for open domain question answering,'' in \emph{Proc. 16th Conf. Eur. Chapter ACL (EACL)}, 2021, pp.~874--880.
\bibitem{maynez2020faithfulness} J. Maynez, S. Narayan, B. Bohnet, and R. McDonald, ``On faithfulness and factuality in abstractive summarization,'' in \emph{Proc. 58th Annu. Meeting ACL}, 2020, pp.~1906--1919.
\bibitem{manakul2023selfcheckgpt} P. Manakul, A. Liusie, and M. J. F. Gales, ``SelfCheckGPT: Zero-resource black-box hallucination detection for generative large language models,'' in \emph{Proc. EMNLP}, 2023, pp.~9004--9017.
\bibitem{min2023factscore} S. Min \emph{et al.}, ``FActScore: Fine-grained atomic evaluation of factual precision in long form text generation,'' in \emph{Proc. EMNLP}, 2023, pp.~12076--12100.
\bibitem{zhong2023poisoning} Z. Zhong, Z. Huang, A. Wettig, and D. Chen, ``Poisoning retrieval corpora by injecting adversarial passages,'' in \emph{Proc. EMNLP}, 2023, pp.~13764--13775.
\bibitem{carlini2024poisoning} N. Carlini \emph{et al.}, ``Poisoning web-scale training datasets is practical,'' in \emph{Proc. IEEE Symp. Security and Privacy (S\&P)}, 2024, pp.~407--425.
\bibitem{owaspllm2025} OWASP Foundation, ``OWASP Top 10 for LLM Applications 2025,'' OWASP GenAI Security Project, 2025. [Online]. Available: https://genai.owasp.org/llm-top-10/
\bibitem{tuomisto2025ethical} T. Tuomisto and L. Harjumaa, ``Ethical considerations of using generative AI in software development,'' in \emph{Proc. 20th Int. Conf. Software Engineering Advances (ICSEA)}, 2025, pp.~53--59.
\bibitem{karhu2025barriers} K. Karhu and J. Kasurinen, ``Barriers and enablers of AI adoption in software testing: A secondary study,'' in \emph{Proc. 20th Int. Conf. Software Engineering Advances (ICSEA)}, 2025, pp.~46--52.
\bibitem{jantti2025digital} M. J\"antti, J. Koponen, and M. Aho, ``How digital experiments support sustainability in a forest machine operator company: A case study,'' in \emph{Proc. 20th Int. Conf. Software Engineering Advances (ICSEA)}, 2025, pp.~1--6.
\end{thebibliography}
